---
title: "Paper Title"
---

# Abstract

> 250-word structured abstract. Background, methods, results, conclusions.

# Introduction

State the gap, the research question, and the contribution of this paper.

# Methods

## Design and sample

Describe the survey design, sampling frame, and sample size. Reference the design object built in `analysis/02-survey-design.R`.

## Inverse probability of treatment weighting

Describe the propensity model, estimand, and balance diagnostics. See `analysis/03-iptw.R` and the [IPTW guide](../guide/iptw.qmd).

## Latent class analysis

Describe the indicator set, model selection criteria, and the chosen number of classes. See `analysis/04-lca.R` and the [LCA guide](../guide/lca.qmd).

## Network analysis

Describe how the network was constructed, the centrality and community-detection methods. See `analysis/05-network.R` and the [network guide](../guide/network.qmd).

## Ethics and data

IRB statement, consent, and data/code availability.

# Results

## Descriptive

```{r}
#| label: tbl-descriptive
#| tbl-cap: "Descriptive characteristics of the sample."
desc <- read.csv(file.path(here::here(), "outputs", "tables", "descriptive.csv"))
gt::gt(desc)
```

## Covariate balance after IPTW

```{r}
#| label: fig-balance
#| fig-cap: "Love plot of standardized mean differences before and after weighting."
knitr::include_graphics(file.path(here::here(), "outputs", "figures", "iptw-balance.png"))
```

## Treatment effect

```{r}
#| label: tbl-effect
#| tbl-cap: "Estimated treatment effect (IPTW)."
eff <- read.csv(file.path(here::here(), "outputs", "tables", "iptw-effects.csv"))
gt::gt(eff)
```

## Latent classes

```{r}
#| label: fig-lca-bic
#| fig-cap: "BIC across candidate LCA models."
knitr::include_graphics(file.path(here::here(), "outputs", "figures", "lca-bic.png"))
```

```{r}
#| label: fig-lca-profiles
#| fig-cap: "Item-response probabilities per latent class."
knitr::include_graphics(file.path(here::here(), "outputs", "figures", "lca-profiles.png"))
```

## Network

```{r}
#| label: fig-network
#| fig-cap: "Network of co-occurrences, colored by community, sized by degree."
knitr::include_graphics(file.path(here::here(), "outputs", "figures", "network.png"))
```

# Discussion

Interpretation, limitations, and implications.

# References

::: {#refs}
:::

# Appendix {-}

## Sensitivity analyses

Describe any sensitivity analyses (e.g. trimming thresholds, alternative LCA K).

## Codebook

Variable definitions and recodes.
